% LaTeX resume using res.cls
\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor} % Allows the definition of hex colors
\usepackage{ifsym}
\usepackage{marvosym} % Required for symbols in the colored box
\usepackage{hyperref}
\setlength{\textwidth}{5.1in} % set width of text portion
\definecolor{linkcolor}{HTML}{506266} % Blue-gray color for links
\hypersetup{colorlinks,breaklinks, urlcolor=linkcolor, linkcolor=linkcolor} % Set up links and colors
\definecolor{light-gray}{gray}{0.9}

\begin{document}

% Center the name over the entire width of resume:
\begin{minipage}[t]{0.7\textwidth}
\moveleft.5\hoffset\centerline{\huge\bf Ang Way Chuang}
\end{minipage}
% Draw a horizontal line the whole width of resume:
% address begins here
% Again, the address lines must be centered over entire width of resume:
\begin{minipage}[t]{0.3\textwidth}
\colorbox{light-gray}{
\begin{tabular}{cl} 
	{\textifsymbol{18}} & \footnotesize 11, Lorong Gemilang Indah 2 \\
 & \footnotesize Taman Gemilang Indah \\
 & \footnotesize 14000, Bukit Mertajam, Penang \\
 {\Mobilefone} & \footnotesize +(60) 018 3267697 \\
 {\Letter} & \footnotesize \href{mailto:wcang79@gmail.com}{wcang79@gmail.com} \\
\end{tabular}
 }
\end{minipage}

\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
\begin{resume}
 
\section{OBJECTIVE}  A position in the field of computer programming with special 
                interests in Linux system programming, Linux kernel development and networking.
 

\section{EDUCATION} {\sl Master of Science} Computer Science (Satellite Communication) \\
		Universiti Sains Malaysia \\
		{\sl Bachelor of Science} Computer Science (Networking) \\
		Universiti Putra Malaysia
                      % \sl will be bold italic in New Century Schoolbook (or
	              % any postscript font) and just slanted in
		      %	Computer Modern (default) font


\section{EXPERIENCE} {\sl Research Associate} \hfill October 2010 - March 2012 \\
                Shonan Fujisawa Campus, Keio University, Kanagawa
                 \begin{itemize}  \itemsep -2pt %reduce space between items
		 \item Responsible for the operation and maintainence of \href{http://www.soi.asia}{SOI Asia} online lecture system.
                 \item Setup and maintained cloud management system.
		 \item Conducted research on IP multicast system and developed a multicast tracer system.
                \end{itemize}
 
                {\sl Research Officer} \hfill            September 2005 - April 2010 \\
                School of Computer Sciences, Universiti Sains Malaysia
                 \begin{itemize}  \itemsep -2pt %reduce space between items
		 \item Conducted research on \href{http://tools.ietf.org/html/rfc3095}{ROHC} and IP network using DVB-S communication
				 and developed a prototype system.
		 \item Responsible for the development and deployment of Satellite Receiver System using 
			 \href{http://tools.ietf.org/html/rfc3077}{LLTM} for the \href{http://www.ai3.net}{AI3} project
		 \item Involved in embedded system (IXP435) development for WiMAX prototype system.
		 \item Involved in operation of SOI Asia lecture on behalf of USM.
                 \end{itemize} 
                {\sl Junior Software Engineer} \hfill        September 2004 - August 2005 \\
                 CEO Consultancy, Kota Kemuning
                  \begin{itemize}
                   \item Developed and maintained camera surveillance server system for SmartVue project.
	           \item Developed for camera surveillance video recorder system.
                   \end{itemize} 
 		{\sl Linux Software Engineer} \hfill        March 2004 -  August 2004 \\
                 Green Packet, Technology Park Malaysia
                  \begin{itemize}
                   \item Conducted research and development on firewall, Internet gateway and Radius protocol.
	           \item Developed and maintained webmin interface for Green Packet's gateway product.
		   \item Enhanced existing 802.1X authenticator
                   \end{itemize} 
\section{COMPUTER \\ SKILLS} {\sl Languages \& Software:} Python, C, Bash, Javascript, Vim, Git, autotools, gdb and various kind of development tools on Linux system.\\
                {\sl Operating Systems:} Linux, Linux and Linux only
	\end{resume} 
\end{document}




